Results visualization across sites

### 2021-11-30 metanalysis_visualization/visualization.Rmd

```{r}
trends_country <- meta_df %>% 
  group_by(country) %>% 
  group_modify( ~ broom::tidy(lm(as.formula(trend_model), data = .x))) %>%
  filter(term == c("periodduring_pandemic:time")) %>% 
  mutate(variance = std.error * std.error) %>% 
  select(country, estimate, variance)

>>>>

```{r}
trends_country <- meta_df %>% 
  filter((time_p >= as.Date("2019-02-01")) & (time_p <= as.Date("2021-05-01"))) %>% 
  group_by(country) %>% 
  group_modify( ~ broom::tidy(lm(as.formula(trend_model), data = .x))) %>%
  filter(term == c("periodduring_pandemic:time")) %>% 
  mutate(variance = std.error * std.error) %>% 
  select(country, estimate, variance)
